%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Academic Tutor} % Job title
    {The Australian National University} % Organization
    {Canberra, Australia} % Location
    {Mar. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Tutoring COMP2550/4450/6445 Advanced Computing R\&D Methods.}
        \item {Taking Charge of AI Planning Topic.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Data Analyst} % Job title
    {The Australian National University} % Organization
    {Canberra, Australia} % Location
    {Jul. 2018 - Nov. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {A data managing and analysis platform for paleo-ecologists.}
        \item {Complex multidimensional data analysis (PCA, CCA, DCA, Regressions).}
        \item {Data visualisation in thesis standard cumulative curves.}
        \item {Developed in R and finished as a Shiny Application, deployed on apache server.}
        \item {Project presented at AQUA (Australasian Quaternary Association) conference 2018.}
        \item {Part of Techlauncher in ANU.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Tech Lead} % Job title
    {Questagame} % Organization
    {Canberra, Australia} % Location
    {Feb. 2018 - Jun. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {A single page web application that identifies the species of birds.}
        \item {Architecture design and scripts for setup and testing.}
        \item {Developed Restful API to share results to front-end.}
        \item {Flask, ReactJS for Interface.}
        \item {Tensorflow model for image recongnition}
        \item {Deployment tested with Docker. Setup tools made with Bash Script.}
        \item {Part of Techlauncher in ANU.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Intern} % Job title
    {Jun Xin Wei Ke Technology LLC} % Organization
    {Beijing, China} % Location
    {Dec. 2017 - Feb. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed data collection framework in Java for a high school thesis information system.}
        \item {Data crawling for the budget assistant system.}
        \item {Helped to develop interfaces with HTML and CSS.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Intern (ES APPS BUS SCVS DEPARTMENT)} % Job title
    {Hewlett Packard Enterprise} % Organization
    {Beijing, China} % Location
    {Dec. 2016 - Feb. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Sales databases maintenance (Salesforce).}
        \item {Python scripts on maintenance.}
        \item {Microsoft Excel and Word to make reports.}
      \end{cvitems}
    }

%---------------------------------------------------------
  
%---------------------------------------------------------
\end{cventries}
